
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Full Papers / Articles \dotfill}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
%---------------------------------------------------------
\vspace{-15pt}
  \cventry
    {}
    {}
    {}
    {}
    {\textbf{Iacovos G. Kolokasis}, Anastasios Papagiannis, Foivos
    Zakkak, Polyvios Pratikakis, and Angelos Bilas.%
    Say Goodbye to Off-heap Caches! On-heap Caches Using Memory-Mapped
    I/O. In Presented as part of the 12th USENIX Workshop on Hot
    Topics in Storage and File Systems (HotStorage '20), Boston, MA,
    2020. USENIX. (\textbf{Best Presentation Award})}
  {}
  \cventry
    {}
    {}
    {}
    {}
    {\textbf{Iacovos G. Kolokasis} and Polyvios
  Pratikakis. Cut to Fit: Tailoring the Partitioning to the
  Computation. 2nd Joint International Workshop on Graph Data
  Management Experiences \& Systems (GRADES) and Network Data
  Analytics (NDA), June 30-July 2019, Amsterdam, Netherlands}
  {}

%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Posters \dotfill}

\vspace{-15pt}
\begin{cventries}
%---------------------------------------------------------

  \cventry
    {}
    {}
    {}
    {}
    {\textbf{Iacovos G. Kolokasis}, Anastasios Papagiannis, Foivos
    Zakkak, Polyvios Pratikakis, and Angelos Bilas.% Garbage
    Collection or Serialization? Between a Rock and a Hard Place! 
    16th International Summer School on Advanced Computer Architecture
    and Compilation for High-Performance and Embedded Systems
    (ACACES).}
  {}

%---------------------------------------------------------
\end{cventries}
      
%---------------------------------------------------------
\cvsubsection{Technical Reports \dotfill}

\vspace{-15pt}
\begin{cventries}
%---------------------------------------------------------

  \cventry
    {}
    {}
    {}
    {}
    {\textbf{Iacovos G. Kolokasis} and Polyvios Pratikakis.
      Cut to Fit: Tailoring the Partitioning to the Computation.
      Technical Report 469, ICS -- FORTH, Apr 2018 }{}%


%---------------------------------------------------------
\end{cventries}
